% Chapter2 Preliminaries
% 2.1 Basic Algebraic Concepts
\newcommand\signature{\index{signature!!}signature}
\newcommand\signatureofbooleans{\index{signature!signature of booleans!}signature of \textit{booleans}}
\newcommand\standardsignature{\index{signature!standard signature!}standard signature}
\newcommand\manysortedsignatures{\index{many-sorted signatures|see{signature}}many-sorted signatures}
\newcommand\Nstandardsignature{\index{signature!standard signature!N-standard signature}N-standard signature}
\newcommand\SigmamathcalR{\index{signature!standard signature!N-standard signature!$\Sigma(\mathcal{R})$}$\Sigma(\mathcal{R})$}

\newcommand\sigmaalgebra{\index{algebra!$\Sigma$-algebra}$\Sigma$-algebra}
\newcommand\standardalgebra{\index{algebra!standard algebra}standard algebra}
\newcommand\Nstandardalgebra{\index{algebra!standard algebra!N-standard algebra}N-standard algebra}
\newcommand\topologicalpartialalgebra{\index{algebra!$\Sigma$-algebra!topological (partial) algebra}topological partial algebra}
\newcommand\mathcalR{\index{algebra!$\Sigma$-algebra!topological (partial) algebra!$\mathcal{R}$}$\mathcal{R}$}

% 2.2 WhileCC programming Language
\newcommand\WhileCCprogramminglanguage{\index{\WhileCC($\Sigma$) programming language}\WhileCC($\Sigma$) programming language}
\newcommand\WhileCCprogramminglanguagesyntax{\index{\WhileCC($\Sigma$) programming language!syntax}\WhileCC($\Sigma$) programming language syntax}
\newcommand\WhileCCprogramminglanguagesemantics{\index{\WhileCC($\Sigma$) programming language!semantics}\WhileCC($\Sigma$) programming language semantics}
\newcommand\WhileCCcomputable{\index{computability!\WhileCC{} computability on $\Nats$}\WhileCC-computable}
\newcommand\WhileCCapproximability{\index{approximability!\WhileCC{}-approximability}\WhileCC-approximability}
\newcommand\WhileCCapproximable{\index{approximability!\WhileCC{}-approximability}\WhileCC-approximable}
\newcommand\realizabilityrelation{\index{realizability relation}realizability relation}
\newcommand\assembly{\index{realizability relation!assembly}assembly}
\newcommand\Computabilityonassemblies{\index{computability!on assemblies}Computability on assemblies}

\newcommand\Realizabilityrelationonnats{\index{realizability relation!on $\Nats$}Realizability relation on $\Nats$}
\newcommand\RealizabilityrelationonRationals{\index{realizability relation!on $\Rationals$}Realizability relation on $\Rationals$}
\newcommand\RealizabilityrelationonCartesianproduct{\index{realizability relation!on Cartesian product}Realizability relation on Cartesian product}
\newcommand\Realizabilityrelationonsequences{\index{realizability relation!on sequences}Realizability relation on sequences}
\newcommand\WelldefinedWhileCCprocedures{\index{\WhileCC($\Sigma$) programming language!well-definedness}Well-defined \WhileCC-procedures}

% 2.3 alpha-tracking

\newcommand\standardenumeration{\index{standard enumeration}standard enumeration}
\newcommand\alphacomputablefunction{\index{computability!$\alpha$-computability!$\alpha$-computable function}$\alpha$-computable function}
\newcommand\alphacomputablereals{\index{computability!$\alpha$-computability!$\alpha$-computable reals $\Reals_c$}$\alpha$-computable reals}
\newcommand\alphacomputablereal{\index{computability!$\alpha$-computability!$\alpha$-computable real}$\alpha$-computable real}
%  2.4 Open exhaustions, Continuity
\newcommand\openexhaustion{\index{open exhaustion}open exhaustion}
\newcommand\effectiveopenexhaustion{\index{open exhaustion!effective open exhaustion}effective open exhaustion}
\newcommand\effectivelylocallyuniformlycontinuous{\index{continuity!effective local uniform continuiuty}effectively locally uniformly continuous}
\newcommand\acceptable{\index{acceptable function}acceptable}

% 2.5 Multipolyomial
\newcommand\multipolynomial{\index{multipolynomial}multipolynomial}
\newcommand\effectivesequenceofmultipolynomials{\index{multipolynomial!effective sequence of multipolynomials}effective sequence of multipolynomials}
\newcommand\effectivelylocallymultipolynomiallyapproximable{\index{approximability!multipolynomial approximability}effectively locally multipolynomially approximable}
\newcommand\GLcomputable{\index{computability!GL-computable}GL-computable}
\newcommand\GrzegorczykLacomecomputability{\index{Grzegorczyk-Lacome computability|see{GL-Computable}}Grzegorczyk-Lacome computability}


% 2.6 Elem Functions
\newcommand\elementaryfunctions{\index{elementary functions}elementary functions}
\newcommand\elementaryfunction{\index{elementary functions}elementary function}

% 4.1 
\newcommand\openncube{\index{$n$-cube!open $n$-cube}open $n$-cube}
\newcommand\closedncube{\index{$n$-cube!closed $n$-cube}closed $n$-cube}
\newcommand\rationalopenncube{\index{$n$-cube!rational open $n$-cube}rational open $n$-cube}
\newcommand\rationalclosedncube{\index{$n$-cube!rational closed $n$-cube}rational closed $n$-cube}

\newcommand\Generalizedopenexhaustion{\index{open exhaustion!generalized to $\Reals^n$}Generalized open exhaustion}
\newcommand\Effectivesequenceofopenexhaustions{\index{open exhaustion!generalized to $\Reals^n$!effective sequence of open exhaustions}Effective sequence of open exhaustions}
\newcommand\simpleeffectiveopenexhaustion{\index{simple effective open exhaustion}simple effective open exhaustion}
\newcommand\RealizabilityrelationonmathbbIton{\index{realizability relation!on $\mathbb{I}^n$}Realizability for $\mathbb{I}^n$}



% 5.3 Continuity for Composition 
\newcommand\forwardcoverageproperty{\index{forward coverage property}forward coverage property}
\newcommand\intervalforwardcoverageproperty{\index{interval forward coverage property}interval forward coverage property}


\newcommand\effectivelyOpen{exhaustion-reflecting\index{exhaustion-reflecting}}
\newcommand\EffectiveOpenness{Exhaustion-reflection\index{exhaustion-reflecting}}
\newcommand\WhileCC{\textit{\textbf{WhileCC}}}
