Honestly, I couldn’t have made it through this without some incredible people in my life -- it truly took a village to write this thesis. Thank you all so much!

First and foremost, my deepest thanks go to Dr. Jeffery Zucker and Dr. Wolfram Kahl.

Dr. Zucker, thank you for all your help and support during my studies. Without your belief in me, I wouldn’t have made it here -- quite literally. You trusted me when I wasn’t even sure I could trust myself, and because of that, I’m in a much better place today. And a special thank you to your wife, Shirley, for her warmth and kindness throughout the years -- it never went unnoticed.

Dr. Kahl, you have been there for me since the start of my degree, always encouraging and helping me in every way imaginable. Thank you for being someone I could always count on! I also truly appreciate your careful and thorough review of my thesis draft and the valuable comments you provided. I seriously couldn't have done this without you. I will always be grateful.

Anthony, my dearest, I honestly can’t imagine getting through this without you. You’ve truly been my rock every step of the way. I’m beyond grateful for everything you’ve done. Also, a huge thank you to your parents, Sheila and George -- your kindness, support, and love made such a difference, and I'm deeply thankful.

To my brothers and my dad, thank you for always being there for me. Your support, your check-ins, and just knowing you were cheering me on from a distance meant more than you know. Sorry for all the ``\textit{Can’t talk, still working on my thesis\ldots}'' messages -- you know I‌ still love you guys, right?

To my closest friends, Anana (yes, her name is Anahita, but I like to call her Anana, as in a pineapple!), Ghazal, and Alireza -- thank you for being there through every meltdown, crisis, and weird late-night rant. You’ve seen me at my worst and still pushed me forward. I’m so lucky to have had you all in my corner.

To my manager at Huawei, Dr. Bingzhou Zheng, thank you for your understanding, support, and flexibility during my co-op -- especially around the time of my back surgery. Your support made a difficult time much easier, and I truly appreciate it.

Finally, a huge thank you to Dr. Franya Franek and (again) Dr. Wolfram Kahl for being on my committee, carefully reading my thesis, providing thoughtful feedback and detailed suggestions, and sitting through my defense with grace (and minimal yawning). I truly appreciate your time and support.