\chapter{Conclusion and Future Work}
\label{sec::ConclusionAndFutureWork}
    The contributions of this thesis are as follows:
    \begin{itemize}
        \item We prove that all elementary functions are \WhileCC-approximable.
        \item We prove that all elementary functions are acceptable.
        \item We present an alternative characterization of acceptable functions.
    \end{itemize}
The following interesting problems are still left open:
\begin{itemize}
    \item Determining the status of the generalized elementary functions to more than one argument:
        In particular, we would like to know if the generalized elementary functions are acceptable, considering the generalized version of acceptability given by \citet{AbstractVSConcreteComputationOnMetricPartialAlgebras_TuckerZucker_2004}. Our idea of decomposing addition and multiplication in Section \ref{sec::deconstruction-addition-multiplication} seems to show us a way forward towards proving that non-unary elementary functions are acceptable. 
    \item Determining the status of the While*-approximability \index{approximability!While*-approximability} model by \citet{ComputationByWhileProgramsOnTopologicalPartialAlgebras_TuckerAndZucker}, i.e., \WhileCC-approximability in the absence of the countable choice operator:
        The nondeterministic choice seems to be an important feature in the \WhileCC{} programming language. But we would also like to know how much power exactly we are adding to our language when adding this nondeterministic choice operator.
    \item
     Extending the equivalence theorem in \citet{ModelOfCompForPartFunc_MingQuanFuAndJeffZucker} to acceptable partial functions of type $\Reals^m\to\Reals$.
\end{itemize}
We also conjecture that all partial unary \WhileCC-approximable functions are acceptable. We would also like to know the answer to the following questions:
\begin{itemize}
        \item If the conjecture holds, are \emph{non-unary} \WhileCC-approximable functions acceptable?
        \item  If the conjecture does not hold, what is a model of computation that characterizes exactly the class of acceptable functions?
\end{itemize}
